### 2023-05-08 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
Documentation

\chapter{Trials and failures}

\section{Machine Learn}

I've tried to create a database with the samples of current. Each sample was a vector with 50k values corresponding a 0.5s of data collected in a 100KHz oscilloscope. And in a second column its

\subsection{Spectogram analysis}

>>>>

\chapter{System Details}

The electroplating system itself is a marginally stable system, depending on various parameters in the correct range to achieve a desired mode.
The tips bellow were used and can help avoid noise and stabilize the system.

- Don't use the oscilloscope with the charger. The charger brings noise from the power line.
- To aviod mechanical noise in the pumping machine use the syringe pump inclined with a bubble.
- external electrical noise collected by antennas or connections.
- To stabilize internal humidity you can turn on the gas pipeline with air into the chamber.

The picture in figure \ref{fig:setup_pic}

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
  \caption{EHDA automation system setup}
  \label{fig:setup_pic}
\end{figure}

\begin{figure}[H]
    \centering
    \resizebox{100mm}{!}{\includegraphics{Figuras/naked_eyes.png}}
    \caption{EHDA picture of the electrified syringe.}
\end{figure}

\section{Setup Validation}
\label{sec:setup_validation}

Initial tests were made to verify the setup assembly and the automation routine integration. In this step I could understand in practice how electrospray works.
It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
Also, liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permittivity. 
 And also physical variables such as flow rate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.

 About the setup, integrate was changed the liquid, nozzle diameter and distance to the plate in order to
make the experiment the most stable and easy to reach cone-jet mode as possible. For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate. Therefore compromising the stabilization in cone jet mode. A solution for that was to increasethe flowrate wich smooths this pumping noise. For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.

\section{Oscilloscope Impedance}
\label{sec:osc_impedance}

The current is being measured by the Oscilloscope using its internal impedance. 
This oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
Selecting one or other can multiply or divide your current measurement by 2. 
By default we are using the 2Mohm differential input. But it was noticed that using the 1Mohm resistance might reduce the noise. 
A proposal of optimization is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-08 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
Documentation

To continue, my proposal would be to prioritize the improvement of the classification step. 
Ideally, we could use machine learning or another algorithm to ensure accurate classification of individual data samples.

By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
In this regard, I would like to present the concept of a fuzzy controller as a potential solution.

To finish, I would propose a final investment in the system portability so that it can be applicable in remote applications.

@@

@@

        One challenge in implementing the controller is that we do not have continuous feedback. 
        Instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

        The fuzzy approach is an attempt to quantify the classification and fit different control models.

        For that, I fuzzyfied the controller input with the data acquired in an experiment of step routine\ref{subsec:step_routine}. With the data, I mapped the area of each spraying mode according to its potential as shown in the Figure \ref{fig:fuzzy_input}.
        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication between the input and output of the controller.

@@

        Our controller is a machine that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules.
        The rules are listed below.

@@

@@

        Note that, for this method to work it is needed to run a step sequence to scan the cone jet stability island. With that data, create the input membership function. Then, run the controller routine in fuzzy mode.

    \subsection{System Portability}
    \label{subsec:portability}

        Raspberry Pi

@@

        The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
        The previous student work was focused in predicting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
        From the development done by me, it highlights the results:

        - Integrate liquid pump to the software and developed a routine with it.

        - Modeled the software to fit a control model turning it easy to implement new control algorithms or experiment routines.

        - Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.

        - Developed a classification for multi jet spraying mode.

        - Developed a simple controller to proof the concept.

        - Optimize the saving of data to a real time streaming together with more sensors' data.

        - Restructured algorithm usability in order to make it more intuitive with the setup file.

>>>>

To continue, my proposal would be to prioritize the improvement of the classification step. 
Ideally, we could use machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
In this regard, I would like to present the concept of a fuzzy controller as a potential solution.

@@

    When it comes to classifying spraying modes, machine learning represents a sophisticated and trendy approach.
    This project was designed in order to substitute our statistical classifier for a more general and accurate algorithm.

    The data collected in this project was saved in 0.5s samples together with its classification allowing it to be used for supervised learning.
    Experimental trials were conducted to explore machine learning algorithms to classify the data. Unfortunately, despite efforts, an accurate method of distinguishing between classifications could not be identified.

@@

        One challenge in implementing the controller in this project is that we don't have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

        The controller project that will be presented is an attempt to quantify the classification and fit it in a fuzzy control model.
        That approach is for an open loop control system and the input and outputs of the controller must be fuzzyfied.

        Firstly, the fuzzyfication and defuzzyfication machines were implemented using the data acquired in the experiment of step routine\ref{subsec:step_routine}, mapping the area of each spraying mode according to its potential.
        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication within the input and output of the controller.

@@

        Our controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules listed below.

@@

        In figure \ref{fig:fuzzyy1}, two tests were made. Test 1 with a higher voltage of 7000V accusing it to be 100\% in multi jet and the output of decrease voltage. Test 2 shows the opposite case when the voltage is lower than expected.

@@

@@

        The works presented in this report represent a continuation and refinement of previous efforts to develop a more precise and versatile automation routine that can be effectively applied in both industrial and research applications.

        The previous student work focused on predicting corona streamers or spark discharges\cite{Monica} and her automation routine provided a valuable proof-of-concept.

        The current project builds on this foundation and highlights several key results, including the integration of a liquid pump into the software and the development of a routine that can be easily modeled to fit a control model, making it straightforward to implement new control algorithms or experiment routines. 
        The software was also remodeled to support threads, allowing for the separation of each subsystem and the exchange of data between them using queue data structures. A classification for multi-jet spraying mode was developed, along with a simple controller to demonstrate proof of concept. 
        Additionally, the saving of data was optimized to a real-time streaming format and expanded to include more sensor data. Finally, the algorithm usability was restructured to make it more intuitive for users through the use of a setup file.

### 2023-05-08 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
Documentation

C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt1} and \ref{fig:multijt2}, the meniscus is not bound to the rim of the capillary. 
This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.

As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray, seen in figure \ref{fig:multijt3}. 
In this work, all modes with more than one stable jet will be classified as multi jet.

>>>>

C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt}, the meniscus is not bound to the rim of the capillary. 
This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray. 
In this work, all modes with more than one stable jet will be classified as multi jet.

### 2023-05-08 Documentation/UFMG/PFCII/Methodology/Methodology.tex
Documentation

This chapter is about describing the methodology and developments to achieve the project goals. 
Firstly, I begin by elaborating on the workings of the classification process in the processing thread. Moving on, I will then delve into the operational sequences of the controller thread. Lastly, I will provide an explanation on the implementation of the controller.

@@

The classification is a key step in our routine and for being able to be used in multipurpose applications our classification routine must be able to run in real-time, which means it must be fast and automatic.
Our goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.

\subsection{Statistical Analysis}
In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
We acquire the current data frame of 0.5s with 100 KHz as sampling frequency. With that each current sample as 50 thousand current values. Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation. Which is referred as the sample standard deviation divided by the sample mean values. 
Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.

>>>>

This chapter is about describing the methodology and developments to achieve the project goals. 
Firstly, by elaborating on the workings of classification process in the processing thread. Moving on, delving into the operational sequences of the controller thread. Lastly, providing an explanation on the implementation of the controller.

@@

The classification is a key step in our routine and for being able to be used in multipurpose applications our classification must be able to run in real-time, which means it must be fast and automatic.
The goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.

\subsection{Statistical Analysis}
In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
We acquire the current data frame of 0.5s with 100 KHz as sampling frequency, with each current sample as 50 thousand current values. Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation. Which is referred as the sample standard deviation divided by the sample mean values. 
Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.
